The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-07-23 paper/ms.tex
Update ack

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. This work uses data
hosted by the Flatiron Institute's FIRE data hub. This project was developed
in part at the 2019 Santa Barbara Gaia Sprint, hosted by the Kavli Institute
for Theoretical Physics (KITP) at the University of California, Santa Barbara.
This research was supported in part at KITP by the Heising-Simons Foundation
and the National Science Foundation (NSF) under Grant No. PHY-1748958. This
work used the Extreme Science and Engineering Discovery Environment (XSEDE),
which is supported by NSF Grant No. OCI-1053575. A.B. was supported in part by
the Roy \& Diana Vagelos Program in the Molecular Life Sciences and the Roy \&
Diana Vagelos Challenge Award. K.V.J.'s contributions were supported in part
by the NSF under Grant No. AST-1614743. M.-M.M.L. was partly supported by the
NSF under Grant No. AST-1815461.

>>>>

\acknowledgments
We thank the anonymous referee for providing helpful comments. We would like
to thank Megan Bedell, Robert A. Benjamin, Maria Bergemann, Joss
Bland-Hawthorn, Tobias Buck, Elena D'Onghia, Benoit Famaey, and Adrian
Price-Whelan for helpful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. This work uses data hosted by the Flatiron
Institute's FIRE data hub. This project was developed in part at the 2019
Santa Barbara Gaia Sprint, hosted by the Kavli Institute for Theoretical
Physics (KITP) at the University of California, Santa Barbara. This research
was supported in part at KITP by the Heising-Simons Foundation and the
National Science Foundation (NSF) under Grant No. PHY-1748958. This work used
the Extreme Science and Engineering Discovery Environment (XSEDE), which is
supported by NSF Grant No. OCI-1053575. A.B. was supported in part by the Roy
\& Diana Vagelos Program in the Molecular Life Sciences and the Roy \& Diana
Vagelos Challenge Award. K.V.J.'s contributions were supported in part by the
NSF under Grant No. AST-1614743. M.-M.M.L. was partly supported by the NSF
under Grant No. AST-1815461.
